Revisiting Short-Chain Fatty Acids and the Microbiota in Colorectal Tumors

### 2018-06-04 submission/manuscript.Rmd
update figure legends

**Figure 1. Using HPLC no change in SCFA measurements was observed between normal, adenoma, and carcinoma individuals.** Acetate concentrations in fecal samples of individuals with normal colons, adenomas, and carcinomas (A). Butyrate concentrations in fecal samples of individuals with normal colons, adenomas, and carcinomas (B). Propionate concentrations in fecal samples of individuals with normal colons, adenomas, and carcinomas (C). The black links indicate the median SCFA concentration. Acetate concentrations in fecal samples before and after treatment for adenoma (yellow) and carcinoma (red) (D). Butyrate concentrations in fecal samples before and after treatment for adenoma (yellow) and carcinoma (red) (E). Propionate concentrations in fecal samples before and after treatment for adenoma (yellow) and carcinoma (red) (F). The black dots and lines represent the median change in SCFA concentration.

**Figure 2. SCFAs do not improve OTU-based Random Forest models.** Difference between the area under the curve of 100 different 80/20 split OTU-based normal versus adenoma 10-fold CV models with and without SCFAs (A). Difference between the area under the curve of 100 different 80/20 OTU-based normal versus carcinoma 10-fold CV models with and without SCFAs (B). The black linke represents the median AUC. The dotted line highlights an AUC of 0.5.

**Figure 3. No change in butyrate producing genes identified between normal, adenoma, and carcinoma individuals.** Imputed gene relative abundance of important butyrate pathway genes using PICRUSt (A). Counts per million (corrected for size and number of contigs in an OPF) for the Butyrate Kinase gene (B). The other genes from the PICRUSt analysis did not align to any of the OPFs in the metagenome analysis.

@@

**Figure S1. OTU-based Random Forest models of SCFA concentrations.** Classification Random Forest train and tests of 100 different 80/20 OTU-based models with 10-fold CV based on higher or lower than the medain SCFA concentration (A). The top 10 OTUs based on mean decrease in accuracy (MDA) for each model, colored by their lowest taxonomic identification (B). Regression Random Forest train and tests of 100 different 80/20 OTU-based models with 10-fold CV based on correlation to actual SCFA concentration (C). The top 10 OTUs based on mean decrease in accuracy (MDA) for each model, colored by their lowest taxonomic identification (D).

>>>>

**Figure 1. No change in SCFA measurements was observed between normal, adenoma, and carcinoma individuals using HPLC.** Acetate concentrations in fecal samples of individuals with normal colons, adenomas, and carcinomas (A). Butyrate concentrations in fecal samples of individuals with normal colons, adenomas, and carcinomas (B). Propionate concentrations in fecal samples of individuals with normal colons, adenomas, and carcinomas (C). The black lines indicate the median SCFA concentration. Acetate concentrations in fecal samples before and after treatment for adenoma (yellow) and carcinoma (red) (D). Butyrate concentrations in fecal samples before and after treatment for adenoma (yellow) and carcinoma (red) (E). Propionate concentrations in fecal samples before and after treatment for adenoma (yellow) and carcinoma (red) (F). The black dots and lines represent the median change in SCFA concentration.

**Figure 2. SCFAs do not improve OTU-based Random Forest models.** The area under the curve of 100 different 80/20 split OTU-based normal versus adenoma 10-fold CV models with and without SCFAs (A). The area under the curve of 100 different 80/20 OTU-based normal versus carcinoma 10-fold CV models with and without SCFAs (B). The black line represents the median AUC. The dotted line highlights an AUC of 0.5.

**Figure 3. No change in butyrate producing genes identified between normal, adenoma, and carcinoma individuals.** Imputed gene relative abundance of important butyrate pathway genes using PICRUSt (A). Counts per million (corrected for size and number of contigs in an OPF) for the Butyrate Kinase gene (B). The other butyrate pathway genes from the PICRUSt analysis did not align to any of the OPFs in the metagenome analysis.

@@

**Figure S1. OTU-based Random Forest models of SCFA concentrations.** The train and test results of 100 different 80/20 OTU-based models with 10-fold CV based on higher or lower than the medain SCFA concentration using classification Random Forest (A). The top 10 OTUs based on mean decrease in accuracy (MDA) for each model, colored by their lowest taxonomic identification (B).

### 2018-06-04 submission/manuscript.tex
update figure legends

\textbf{Figure 1. Using HPLC no change in SCFA measurements was observed
between normal, adenoma, and carcinoma individuals.} Acetate
concentrations in fecal samples of individuals with normal colons,
adenomas, and carcinomas (A). Butyrate concentrations in fecal samples
of individuals with normal colons, adenomas, and carcinomas (B).
Propionate concentrations in fecal samples of individuals with normal
colons, adenomas, and carcinomas (C). The black links indicate the
median SCFA concentration. Acetate concentrations in fecal samples
before and after treatment for adenoma (yellow) and carcinoma (red) (D).
Butyrate concentrations in fecal samples before and after treatment for
adenoma (yellow) and carcinoma (red) (E). Propionate concentrations in
fecal samples before and after treatment for adenoma (yellow) and
carcinoma (red) (F). The black dots and lines represent the median
change in SCFA concentration.

\textbf{Figure 2. SCFAs do not improve OTU-based Random Forest models.}
Difference between the area under the curve of 100 different 80/20 split
OTU-based normal versus adenoma 10-fold CV models with and without SCFAs
(A). Difference between the area under the curve of 100 different 80/20
OTU-based normal versus carcinoma 10-fold CV models with and without
SCFAs (B). The black linke represents the median AUC. The dotted line
highlights an AUC of 0.5.

\textbf{Figure 3. No change in butyrate producing genes identified
between normal, adenoma, and carcinoma individuals.} Imputed gene
relative abundance of important butyrate pathway genes using PICRUSt
(A). Counts per million (corrected for size and number of contigs in an
OPF) for the Butyrate Kinase gene (B). The other genes from the PICRUSt
analysis did not align to any of the OPFs in the metagenome analysis.

@@

\textbf{Figure S1. OTU-based Random Forest models of SCFA
concentrations.} Classification Random Forest train and tests of 100
different 80/20 OTU-based models with 10-fold CV based on higher or
lower than the medain SCFA concentration (A). The top 10 OTUs based on
mean decrease in accuracy (MDA) for each model, colored by their lowest
taxonomic identification (B). Regression Random Forest train and tests
of 100 different 80/20 OTU-based models with 10-fold CV based on
correlation to actual SCFA concentration (C). The top 10 OTUs based on
mean decrease in accuracy (MDA) for each model, colored by their lowest
taxonomic identification (D).

>>>>

\textbf{Figure 1. No change in SCFA measurements was observed between
normal, adenoma, and carcinoma individuals using HPLC.} Acetate
concentrations in fecal samples of individuals with normal colons,
adenomas, and carcinomas (A). Butyrate concentrations in fecal samples
of individuals with normal colons, adenomas, and carcinomas (B).
Propionate concentrations in fecal samples of individuals with normal
colons, adenomas, and carcinomas (C). The black lines indicate the
median SCFA concentration. Acetate concentrations in fecal samples
before and after treatment for adenoma (yellow) and carcinoma (red) (D).
Butyrate concentrations in fecal samples before and after treatment for
adenoma (yellow) and carcinoma (red) (E). Propionate concentrations in
fecal samples before and after treatment for adenoma (yellow) and
carcinoma (red) (F). The black dots and lines represent the median
change in SCFA concentration.

\textbf{Figure 2. SCFAs do not improve OTU-based Random Forest models.}
The area under the curve of 100 different 80/20 split OTU-based normal
versus adenoma 10-fold CV models with and without SCFAs (A). The area
under the curve of 100 different 80/20 OTU-based normal versus carcinoma
10-fold CV models with and without SCFAs (B). The black line represents
the median AUC. The dotted line highlights an AUC of 0.5.

\textbf{Figure 3. No change in butyrate producing genes identified
between normal, adenoma, and carcinoma individuals.} Imputed gene
relative abundance of important butyrate pathway genes using PICRUSt
(A). Counts per million (corrected for size and number of contigs in an
OPF) for the Butyrate Kinase gene (B). The other butyrate pathway genes
from the PICRUSt analysis did not align to any of the OPFs in the
metagenome analysis.

@@

\textbf{Figure S1. OTU-based Random Forest models of SCFA
concentrations.} The train and test results of 100 different 80/20
OTU-based models with 10-fold CV based on higher or lower than the
medain SCFA concentration using classification Random Forest (A). The
top 10 OTUs based on mean decrease in accuracy (MDA) for each model,
colored by their lowest taxonomic identification (B).
